### 2022-11-24 dissertation/chapters/08-results.tex
✨ (final-review): Up to chapter 4

\chapter{Results}
\label{chap:results}

\begin{quotation}
	\noindent ``Without data, you are just another person with an opinion.''
\end{quotation}
\begin{flushright}
	- W. Edwards Deming
\end{flushright}

The last step in the scientific process requires the presentation of the outcomes of the empirical process. Objective discussions based on statistical analysis of the findings is required. The design and methodology of the empirical process was presented in Chapter~\ref{chap:methodology}. The methodology presented a number of experimental groups to conduct. The experimental groups that were identified include a case study on the behaviour of the \acs{BHH} during training, an empirical comparison to the performance of state-of-the-art, standalone, low-level \index{heuristic}heuristics, and a number of experiments related to the empirical testing of the effects of hyper-parameters on the outcomes of the \acs{BHH}.

This chapter provides the outcomes of the empirical processes and provides results on all the experiments that have been conducted. Detailed discussions follow on the outcomes of each experiment. Discussions are accompanied by figures and plots to help provide visual aid for discussions. The output of the statistical analysis that yielded the results is provided in Appendix~\ref{app:statistical_analysis}. The remainder of the chapter is structured as follows.

\begin{itemize}
	\item \textbf{Section \ref{sec:results:overview}} provides a brief overview of the outcomes of the empirical process and highlights key aspects to observe in the results.

	\item \textbf{Section \ref{sec:results:case_study}} provides detailed discussions on the outcomes of the case study on the behaviour of the \acs{BHH}. Illustrations are provided to show the change in parameter values to illustrate the outcomes of the learning process of the \acs{BHH}, while training the underlying \acf{FFNN}.

	\item \textbf{Section \ref{sec:results:standalone}} provides the results of the performance of the \acs{BHH} compared to individual low-level \index{heuristic}heuristics on all datasets. Three variants of the \acs{BHH} are included in these results. These include the baseline configuration, as well as a configuration that only includes gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration that only includes meta-heuristics in the \index{heuristic pool}heuristic pool.

	\item \textbf{Section \ref{sec:results:heuristic_pool}} provides the results for the experimental group that analyses the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:population}} provides the results for the experimental group that analyses the effects of the \textit{population size} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:credit}} provides the results for the experimental group that analyses the effects of the \textit{credit assignment strategy} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:reselection}} provides the results for the experimental group that analyses the effects of the \textit{reselection interval} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:replay}} provides the results for the experimental group that analyses the effects of the \textit{replay window size} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:reanalysis}} provides the results for the experimental group that analyses the effects of the \textit{reanalysis interval} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:burn_in}} provides the results for the experimental group that analyses the effects of the \textit{burn in window size} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:normalise}} provides the results for the experimental group that analyses the effects of the \textit{normalisation} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:discounted_rewards}} provides the results for the experimental group that analyses the effects of the \textit{discounted rewards} hyper-parameter on the outcomes of the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:summary}} provides a brief summary of the chapter.
\end{itemize}

\section{Overview}\label{sec:results:overview}

This section provides a brief discussion on the general outcome of the empirical process as a whole. Overall the \acs{BHH} is shown to successfully train the underlying \acp{FFNN} for all datasets. In general, the \acs{BHH} performs well and the empirical process provides key insights into the workings of the \acs{BHH}. Where possible, a number of improvements to the \acs{BHH} are identified and recommended as it relates to the outcomes of the results.

Given the nature of the \acs{BHH}, it is recommended that the following aspects be kept in mind when observing the results. The \acs{BHH} applies a form of \index{online learning}online learning. As such, the \acs{BHH} applies the learning mechanism during training in a single run of the training process. The training process is not repeated iteratively. All experiments conducted are executed for 30 epochs. The number of training steps executed is dependent on the batch size applied for each dataset.

All of the underlying \acp{FFNN} trained in the empirical process are relatively small. As such, most of the training progress is observed to occur withing the first five epochs. As a result, the \acs{BHH} should apply most learning at the early stages of the training process. After five epochs, the training of most of the underlying \acp{FFNN} converges and little performance gain is observed after that point. Since this empirical process does not apply early stopping of the training process, the \acs{BHH} will continue to explore the \index{heuristic}heuristic space beyond the five epoch mark.

The \acs{BHH} does not implement a move acceptance strategy, where the application of a heuristic to an entity is only accepted if it leads to a better solution. In some cases the \acs{BHH} then selects heuristics that yield sub-optimal results, but is shown to mostly return to optimal solutions over a number of steps.

Given the stochastic nature of the \index{heuristic}heuristic selection mechanism, sufficient samples of the performance of each heuristics-entity combination in the performance log is required for the \acs{BHH} to learn. This requirement is further strengthened by the Bayesian nature of the probabilistic model implemented by the \acs{BHH}. The probabilistic model implements \textit{probabilities of heuristic selection probabilities} and as such, insufficient samples in the performance log could render a form of random search.

The \textit{reanalysis interval} defines intervals at which the \acs{BHH} reanalyses the performance log, in effect, resetting the concentration parameters to their default values and reapplying the underlying Bayesian analysis process on the performance log. Furthermore, the \textit{replay window size} defines the amount of performance evidence in the performance log. By default, the \acs{BHH} baseline configuration has a reanalysis interval of 10, and a replay window size of 10, which is a small window to learn from. Despite the small reanalysis interval and the small replay window size, it should be observed that the \acs{BHH} exploits small performance biases regardless and does find small performance gains throughout.

\section{Behavioural Case Study}\label{sec:results:case_study}

This section provides the empirical results of the case study on the behaviour of the \acs{BHH} as it is used to train a \acs{FFNN} on the iris dataset. As a reminder, the iris dataset contains 150 records, split into a training dataset containing 120 records, and a test dataset that contains 30 records. The test dataset is treated like a validation dataset, and is evaluated at every training step to illustrate the outcomes of the \acs{BHH} throughout the training process. Mini-batch training is executed with a batch size of 30. The results that are presented are averaged over 30 independent runs.

Furthermore, the case study focuses on three variants of the \acs{BHH}. These include the baseline configuration, as was provided in Chapter~\ref{chap:bhh} and is denoted as bhh\_baseline (illustrated throughout in \textcolor{red}{red}). Furthermore, the case study also includes a configuration of the \acs{BHH} that has a ``long memory'' by setting the \textit{replay window size} hyper-parameter to 250, and is denoted as bhh\_replay\_250 (illustrated throughout in \textcolor{green}{green}). Finally, the case study includes a configuration that makes use of the \textit{symmetric} credit assignment strategy hyper-parameter, and is denoted as bhh\_credit\_symmetric (illustrated throughout in \textcolor{blue}{blue}).

These configurations were specifically chosen for the following reasons: the large replay window size configuration is chosen to illustrate a case where the \acs{BHH} does not ``forget'' past performances of the low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the configuration that utilises the symmetric credit assignment strategy is chosen to illustrate a case where there \acs{BHH} does not reward good performance, and does not yield a bias towards \index{heuristic}heuristics that perform well at all. This section is structured as follows.

\begin{itemize}
	\item \textbf{Section \ref{sec:results:case_study:performance_metrics}} provides illustrations and discussions around the outcomes of the performance metrics as obtained by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:concentration_parameters}} provides illustrations and discussions around the changes in concentration parameter values as a result of the learning mechanism implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:probs_of_select_probs}} provides illustrations and discussions around the changes in the \textit{probabilities of \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:prior_selec_prob}} provides illustrations and discussions around the changes in the \textit{prior \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.

	\item \textbf{Section \ref{sec:results:case_study:posterior_selec_prob}} provides illustrations and discussions around the changes in the \textit{posterior \index{heuristic}heuristic selection probabilities} as a result of the learning mechanism implemented by the \acs{BHH}.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% METRICS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Performance Metrics}\label{sec:results:case_study:performance_metrics}

This section provides illustrations and discussions around the outcomes of the train and test performance metrics as obtained by the \acs{BHH}. Figures~\ref{fig:results:case_study:metrics:train_loss}-\ref{fig:results:case_study:metrics:test_accuracy} provide illustrations of the train and test, loss and accuracy plots of the \acs{BHH} over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_loss.pdf}
		\caption{Train log loss}
		\label{fig:results:case_study:metrics:train_loss}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_loss.pdf}
		\caption{Test log loss}
		\label{fig:results:case_study:metrics:test_loss}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/train/train_accuracy.pdf}
		\caption{Train log accuracy}
		\label{fig:results:case_study:metrics:train_accuracy}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/metrics/figures/test/test_accuracy.pdf}
		\caption{Test log accuracy}
		\label{fig:results:case_study:metrics:test_accuracy}
	\end{subfigure}
	\par\bigskip
	\caption{The average train and test, loss and accuracy plots over 30 epochs, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:metrics}
\end{figure}

The first logical observation that can be made is that the \acs{BHH} was indeed able to successfully train the underlying \acs{FFNN}, observed by the convergence of the training process, yielding good results. Figures~\ref{fig:results:case_study:metrics:train_accuracy} and~\ref{fig:results:case_study:metrics:test_accuracy} show that the trained \acs{FFNN} achieved an accuracy of almost 100\%.

Although the different configurations of the \acs{BHH} are all able to succesfully train the underlying \acs{FFNN}, in this particular case, there is no clear distinction between the performance of any of the configurations under consideration.

The volatility observed in Figure~\ref{fig:results:case_study:metrics:test_loss} is due to overfitting and partly due to the noisiness that results from mini-batch training. Early stopping can be applied to the training process to hault training before the model overfits on the training data. The training dataset is also very small, with just 120 samples. As such, overfitting can be expected.

From Figure~\ref{fig:results:case_study:metrics:train_loss}, at the 22nd epoch, a small divergence of the train loss can be observed. This could simply be a result of momentum that is maintained when switching between low-level \index{heuristic}heuristics in an attempt to find better solutions. For example, momentum can be built up by one of the gradient-based heuristics, after which the \acs{BHH} switches to another heuristic in an attempt to find better solutions. The \acs{BHH} does not incorporate a \textit{move acceptance strategy}, whereby a heuristic's outcome is rejected if it does not improve on previous solutions, yielding a possibly worse loss measurement as it relates to the test set. A move acceptance strategy can be utilised on a validation set as a mechanism to accept or reject heuristic progressions from one step to the other.

Finally, it should be noted that the \acs{BHH} implements learning at every mini-batch step, while Figure~\ref{fig:results:case_study:metrics} only provides the outcomes of performance metrics at the end of each epoch. Further investigation is required at a mini-batch step level and is provided in the following sections.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PARAMS ALPHAS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Concentration Parameters}\label{sec:results:case_study:concentration_parameters}

To illustrate the learning process undergone by the \acs{BHH}, further investigation is required. Consider the concentration parameter $\boldsymbol{\alpha}$ that parameterises the \index{Dirichelet probability distribution}Dirichelet probability distribution, denoted $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$. The probability distribution, $P(\boldsymbol{\theta} \vert \boldsymbol{\alpha})$, is used to sample prior \textit{probabilities of selection probabilities}. Figures~\ref{fig:results:case_study:alphas:0}-\ref{fig:results:case_study:alphas:8} provide illustrations that show that change in values of the concentration parameter $\boldsymbol{\alpha}$, at index 0, 6, 7, and 8 respectively. Index 0, 6, 7, and 8 represent the concentration parameters for the \acs{SGD}, \acs{Adam}, \acs{PSO} and \acs{GA} low-level heuristics respectively, and only represent a subset of the elements in $\boldsymbol{\alpha}$ and thus, the \index{heuristic pool}heuristic pool. Similar illustrations for the other elements in $\boldsymbol{\alpha}$ are left out for brevity as they contain similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[0].pdf}
		\caption{$\alpha_{0}$ - \acs{SGD}}
		\label{fig:results:case_study:alphas:0}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[6].pdf}
		\caption{$\alpha_{6}$ - \acs{Adam}}
		\label{fig:results:case_study:alphas:6}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[7].pdf}
		\caption{$\alpha_{7}$ - \acs{PSO}}
		\label{fig:results:case_study:alphas:7}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=1.0\textwidth]{case_study/params/figures/alphas/alpha[8].pdf}
		\caption{$\alpha_{8}$ - \acs{GA}}
		\label{fig:results:case_study:alphas:8}
	\end{subfigure}
	\par\bigskip
	\caption{The average value of the concentration parameter $\boldsymbol{\alpha}$, at indices 0,6,7, and 8 over 240 steps, obtained from 30 runs of the case study on the behaviour of the \acs{BHH} on the iris dataset, illustrated in log scale.}
	\label{fig:results:case_study:alphas}
\end{figure}

The first logical observation to be made from Figures~\ref{fig:results:case_study:alphas:0}-\ref{fig:results:case_study:alphas:8} is the step-wise, increasing nature of $\boldsymbol{\alpha}$ for the bhh\_replay\_250 configuration, illustrated in \textcolor{green}{green}. Since the replay window size is sufficienty large to contain the performance log for all the steps executed in the training process, the \acs{BHH} does not forget past performances of low-level heuristics at all. The value for $\boldsymbol{\alpha}$ is never reset to its initial value of 1.0, and thus, $\boldsymbol{\alpha}$ continues to increase throughout the training process. However, it should be noted that the rate and degree of change is different for different indices of $\boldsymbol{\alpha}$. The aforementioned observation is the first indicator of the learning process yielded by the \acs{BHH}. Heuristics that perform well will see their corresponding element in $\boldsymbol{\alpha}$ increase more rapidly that other heuristics that do not perform well.

The next observations that can be made are for the bhh\_baseline configuration, illustrated in \textcolor{red}{red}, and the bhh\_credit\_symmetric configuration in \textcolor{blue}{blue}. Both these configurations see $\boldsymbol{\alpha}$ being reset to its initial value of 1.0 as regular intervals. This interval is defined by the \textit{reanalysis interval} hyper-parameter. The reanalysis interval dictates the frequency at which Bayesian analysis is conducated on the performance log, mainted by the \acs{BHH}. Bayesian analysis is used to update $\boldsymbol{\alpha}$ only at the reanalysis interval. As a result, small plateaus appear where $\boldsymbol{\alpha}$ does not change.

>>>>

\chapter{Conclusion}
\label{chap:conclusion}

\begin{quotation}
      ``I am sorry to have made such a long speech, but I did not have time to make a shorter one.''
\end{quotation}
\begin{flushright}
      - Winston Churchill
\end{flushright}

This chapter provides a summary of the research that is done in this dissertation. The research objectives were set out in Chapter \ref{chap:introduction} and are concluded in this chapter. Furthermore, this chapter provides a summary of the results and findings from the empirical process and provides future research opportunities. The remainder of the chapter is structured as follows:

\begin{itemize}
      \item \textbf{Section \ref{sec:conclusion:research_goals}} provides a summary of the research intent and provides a review of the problem statement, objectives and motivations behind the research.

      \item \textbf{Section \ref{sec:conclusion:background_info}} summarises the background information that was covered.

      \item \textbf{Section \ref{sec:conclusion:bhh}} provides a brief summary of the \ac{BHH} and its implementation.

      \item \textbf{Section \ref{sec:conclusion:methodology}} provides a brief summary of the methodology and the empirical process that was followed.

      \item \textbf{Section \ref{sec:conclusion:results}} summarises the research findings. This section is broken down into the various experimental groups that were executed.

      \item \textbf{Section \ref{sec:conclusion:further_research}} presents future research opportunities.

      \item \textbf{Section \ref{sec:conclusion:documentation_and_data}} provides a brief discussion on supporting material related to the research, as made available by the authors.

      \item \textbf{Section \ref{sec:conclusion:summary}} provides a brief summary of the chapter.
\end{itemize}

\section{Summary of Research Intent}
\label{sec:conclusion:research_goals}

This section briefly reviews the problem statement, motivations and research objectives that was set out in Chapter \ref{chap:introduction} of this dissertation.

\subsection{Review of Problem Statement}
\label{sec:conclusion:research_goals:problem_statement}

The main area of focus for the research done in this dissertation stems from the problem statement, which identified the difficult and tedious problem of selecting the best \index{heuristic}heuristic for training \acp{FFNN}. This process is often non-trivial and time-consuming. There is no easy way to know which \index{heuristic}heuristic to select to train \acp{FFNN}. Traditionally, an iterative approach of trial-and-error was followed. This process involves a tedious process of carefully considering and selecting candidate \index{heuristic}heuristics, whereby each candidate \index{heuristic}heuristic is then empirically tested and evaluated. This process is often executed at the expense of the researcher's resources.

\subsection{Review of Research Motivation}
\label{sec:conclusion:research_goals:motivations}

The research presented in this disseration identified the possibility of using a different approach, referred to as \acp{HH}, to automate the \index{heuristic}heuristic selection process. \acp{HH} are high-level search algorithms that search in the \index{heuristic}heuristic space, whereby low-level \index{heuristic}heuristics search in the solution space. \acp{HH} have been shown to provide a general solution to the \index{heuristic}heuristic selection process. The benefit that such an approach provides, is that it automates the \index{heuristic}heuristic selection process. This approach saves researchers time and potentially produce a solution that could generalise to multiple problems.

Investigation was done into the landscapes of existing solutions to train \acp{FFNN} as well as \acp{HH}. Though there exists many applications where \acp{HH} are used for optimisation, there are little to no published work on using \acp{HH} to train \acp{FFNN}. The only work that was found include the work by~\citeauthor{ref:nel:2021}~\cite{ref:nel:2021}.

\subsection{Review of Research Objectives}
\label{sec:conclusion:research_goals:research_objectives}

Existing techniques from other problem domains were considered. \acs{RL}, meta-learning and probabilistic learning approached were considered. Bayesian probability theory showed promise. This research then set out to develop a novel high-level \index{heuristic}heuristic that utilises probability theory in an online learning setting to drive the automatic \index{heuristic}heuristic selection process. As such, the \acs{BHH} was conceptualised. The research objectives were defined and are summarised as follows:

\begin{itemize}
      \item Conduct literature studies on all related topics that are relevant to the development of the \acs{BHH}. These include \acs{ANN}, existing low-level \index{heuristic}heuristics, meta-learning, \acp{HH}, probability theory and Bayesian statistics.

      \item Develop a novel \acs{BHH} that can be used to automate the \index{heuristic}heuristic selection process. The \acs{BHH} follows an approach that includes a selective and perturbative element in an online learning setting. Bayesian statistics and \acs{MAP} is used as the optimisation technique. Furthermore, the \acs{BHH} implements a mapping for proxied \index{heuristic}heuristic state update operations, whereby \index{heuristic}heuristic state is maintained by outsourcing state opertations to relevant low-level \index{heuristic}heuristics.

      \item Conduct an empirical study to show that the \ac{BHH} is able to train \acp{FFNN} effectively on a number of different datasets.

      \item Conduct an empirical study to study the behavioural characteristics of the \acs{BHH}.

      \item Conduct an empirical study to critically evaluate the performance of the \acs{BHH} compared to traditional, low-level, standalone \index{heuristic}heuristic when training \acp{FFNN} on a number of different datasets.

      \item Conduct an empirical study to evaluate variants of the \acs{BHH} to study the impact of various hyper-parameters on the outcomes of the \ac{BHH}.

      \item Provide and discuss the findings of the results produced by the empirical process. The results are analysed for statistical significance.
\end{itemize}

The research objectives set out in this dissertation are extensive. Each of these research objectives have been successfully executed. From the findings made in this dissertation, many different opportunities for future research are identified.

\section{Summary of Background Information}
\label{sec:conclusion:background_info}

Chapters \ref{chap:anns}-\ref{chap:probability} provided the reader with the relevant background information that is necessary to develop the novel \acs{BHH}. Chapter~\ref{chap:anns} provided background information on \acp{ANN}. All the components that make up the \acs{AN} were provided and is followed by discussions on \acp{FFNN}. Chapter~\ref{chap:heuristics} provided background information on various low-level heuristics that are designed to train \acp{FFNN}. A number of gradient-based \index{heuristic}heuristics and \index{meta-heuristic}meta-heuristics were presented in detail. Chapter~\ref{chap:hhs} provided background information and literature reviews on \acp{HH}. Meta-learning is discussed and a \acs{HH} classification scheme, developed by \citeauthor{ref:burke:2010}~\cite{ref:burke:2010}, was discussed in detail. Chapter~\ref{chap:probability} provided background information and mathematical derivations on probability theory and Bayesian statistics. Various probability distributions were provided along with their conjugate priors. \acs{MLE} and \acs{MAP} were presented in detail along with mathematical breakdowns.

From the aforementioned chapters, it can be concluded that the necessary background information was provided as set out in the research objectives of this dissertation.

\section{Summary of The Bayesian Hyper-Heuristic}
\label{sec:conclusion:bhh}

The main contribution from this dissertation is the development of a novel \acf{BHH}. Chapter \ref{chap:bhh} provided the details on the concept and implementation of the \ac{BHH}. Various design decisions and hyper-parameters that could affect the outcomes of the \ac{BHH} were presented.

It was shown that the \acs{BHH} is a population-based, meta-hyper-heuristic that utilises selection and perturbation of low-level \index{heuristic}heuristics in an online learning fashion. \index{heuristic}Heuristics are selected for each entity in a population of entities that each implement a candidate solution to the underlying \acs{FFNN}. The \acs{BHH} uses a Bayesian probabilistic model to drive the \index{heuristic}heuristic selection process. \acs{MAP} was derived for the probabilistic model and is used as the mechanism by which the \acs{BHH} is optimised, yielding the learning capability of the \acs{BHH}.

Furthermore, it is shown that \index{heuristic}heuristic selection alone is not sufficient and that a mechanism of transition between \index{heuristic}heuristics is needed as they are selected for each entity in the population. Entity and \index{heuristic}heuristic state and state-manipulation formed the cornerstone of this topic. Perturbation of \index{heuristic}heuristics and solutions is achieved through a technique that deconstructs \index{heuristic}heuristics into their initialisation and update steps. The update operations for each heuristic was derived as movement equations borrowed from the field of physics. This technique allows for the proxying of update step operations as they are required by different \index{heuristic}heuristics.

Detailed discussions were provided on a number of hyper-parameters that each contribute to the trade-off between \index{heuristic}heuristic and solution exploration and exploitation. These hyper-parameters include the \index{heuristic pool}\textit{heuristic pool} configuration, the \textit{population size}, the \textit{credit assignment strategy} used, the \textit{reselection interval}, the \textit{replay window size}, the \textit{reanalysis interval}, the \textit{burn in window size}, \textit{normalisation} of concentration parameters and \textit{discounted rewards} as assigned by the credit assignment strategy. A \acs{BHH} baseline configuration was identified with default values for each of the hyper-parameters.

It was mentioned that the \acs{BHH}, implemented in this dissertation, does not implement a move acceptance strategy that rejects heuristic progressions if they do not improve on the current best solution. Throughout the presentation of empirical results, it is recommended that this technique be investigated and implemented in further research.

\section{Summary of Methodology}
\label{sec:conclusion:methodology}

The research objectives defined a number of empirical tests to be executed. Each one of the empirical tests is referred to as an experimental group. Various experimental groups have been identified and are listed below.

\begin{itemize}
      \item An experimental group that provides a case-study on the behaviour of the \ac{BHH} as it relates to training of a \acs{FFNN} on an example dataset (iris), in order to understand the workings of the \acs{BHH}, and to determine if the \acs{BHH} is able to successfully train \acp{FFNN}. Three different configurations of the \acs{BHH} configuration was implemented. This includes the default \acs{BHH} baseline configuration, the \acs{BHH} baseline configuration where the replay window size is set to 250, and the \acs{BHH} baseline configuration which utilises the \textit{symmetric} credit assignment strategy.

      \item An experimental group that provides a comparative analysis between the performance of the \acs{BHH} baseline configuration and low-level, standalone \index{heuristic}heuristics when training \acp{FFNN} on a number of datasets.

      \item An experimental group that provides a comparative analysis between variants of the \ac{BHH} that investigate the effects of various hyper-parameters on the outcomes of the \acs{BHH}. These variants include:

            \begin{itemize}
                  \item The \acs{BHH} baseline configuration with different \index{heuristic pool}heuristic pool configurations. Three different \index{heuristic pool}heuristic pool configurations were implemented. These configurations include a configuration with all the low-level \index{heuristic}heuristics included in the \index{heuristic pool}heuristic pool, a configuration with only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and a configuration with only \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool.

                  \item The \acs{BHH} baseline configuration with different population sizes. Five different population sizes were implemented including 5, 10, 15, 20, and 25.

                  \item The \acs{BHH} baseline configuration with different credit assignment strategies. Five different credit assignment strategies were implemented including the \textit{ibest}, \textit{pbest}, \textit{rbest}, \textit{gbest}, and \textit{symmetric} credit assignment strategies.

                  \item The \acs{BHH} baseline configuration with different reselection intervals. Five different reselection intervals were implemented including 1, 5, 10, 15, and 20.

                  \item The \acs{BHH} baseline configuration with different reanalysis window sizes. Five different reanalysis intervals were implemented including 1, 5, 10, 15, and 20.

                  \item The \acs{BHH} baseline configuration with different replay window sizes. Five different replay window sizes were implemented including 1, 5, 10, 15, and 20.

                  \item The \acs{BHH} baseline configuration with different burn in window sizes. Five different burn in window sizes were implemented including 0, 5, 10, 15, and 20.

                  \item The \acs{BHH} baseline configuration where normalisation of pseudo counts for concentration parameters, as derived from credit allocations in the performance log, are enabled and disabled.

                  \item The \acs{BHH} baseline configuration where discounted rewards of pseudo counts for concentration parameters, as derived from credit allocations in the performance log, are enabled and disabled.
            \end{itemize}
\end{itemize}

Each experimental group was executed against a set of fourteen datasets, consisting of regression and classification problems, split between uni- and multimodal problems. Each experimental group was repeated over 30 runs for statistical certainty. The statistical analysis process was discussed and the ANOVA, post hoc Tukey, independent T-test and Kruskal-Wallis statistical tests formed part of the statistical tests that were conducted.

All experimental groups were run for a maximum of 30 epochs in order to allow for the studying of the \ac{BHH} even after training has converged and overfitting has occured. The maximum epoch strategy yielded a training process that is longer than what was empirically found to be necessary. This also meant that no early stopping strategy was used. Future research opportunities should incorporate an early stopping strategy of the training process.

\section{Summary of Results}
\label{sec:conclusion:results}

This section provides a summary of the results obtained from each of the experimental groups that were executed. This section is structured as follows.

\begin{itemize}
      \item \textbf{Section \ref{sec:conclusion:results:summary:case_study}} provides a summary of the results for the experimental group that executed a case study on the behaviour of the \acs{BHH} on an example dataset.

      \item \textbf{Section \ref{sec:conclusion:results:summary:standalone}} provides a summary of the results for the experimental group that compares the performance of the \acs{BHH} baseline configuration with low-level, standalone \index{heuristic}heuristics, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:heuristic_pool}} provides a summary of the results for the experimental group that investigates the effects of the \index{heuristic pool}\textit{heuristic pool} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:population_size}} provides a summary of the results for the experimental group that investigates the effects of the \textit{population size} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:credit}} provides a summary of the results for the experimental group that investigates the effects of the \textit{credit assignment strategy} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:reselection}} provides a summary of the results for the experimental group that investigates the effects of the \textit{reselection interval} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:replay}} provides a summary of the results for the experimental group that investigates the effects of the \textit{replay window size} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:reanalysis}} provides a summary of the results for the experimental group that investigates the effects of the \textit{reanalysis interval} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:burn_in}} provides a summary of the results for the experimental group that investigates the effects of the \textit{burn in window size} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:normalise}} provides a summary of the results for the experimental group that investigates the effects of the \textit{normalisation} hyper-parameter on the \acs{BHH}, across all datasets.

      \item \textbf{Section \ref{sec:conclusion:results:summary:discounted_rewards}} provides a summary of the results for the experimental group that investigates the effects of the \textit{discounted rewards} hyper-parameter on the \acs{BHH}, across all datasets.
\end{itemize}

\subsection{Behavioural Case Study}
\label{sec:conclusion:results:summary:case_study}

For this experimental group it was found that the \ac{BHH} is able to train a \acf{FFNN} relatively well. Detailed analysis was provided for various state parameters maintained by the \acs{BHH}. These include the concentration parameters for different heuristics, probabilities of \index{heuristic}heuristic selection probabilities, prior heuristic selection probabilities and posterior heuristic selection probabilities. It was shown that the \ac{BHH} is able to learn and that the \acs{BHH} is able to exploit small performance biases as it relates to \index{heuristic}heuristic selection. This enables the \acs{BHH} to select the correct \index{heuristic}heuristics to apply to the correct entities at the correct time in the training process.

Various illustrations of the train and test loss plots, as it relates to training of a \acs{FFNN} on the the iris dataset, have been provided. Furthermore, various illustrations on the changes of the \acs{BHH} state parameters were provided for visual aid.

The main findings that were made for this experimental group are given as follows. Most of the training progression is made in the early stages of the training process. That leads to the conclusion that the \acs{BHH} has a small window from which it should learn and gain the most in the training process. After training has converged, the \acs{BHH} resets its concentration parameters and heuristic selection returns to the symmetric heuristic selection case. As such, the \acs{BHH} explores other heuristics in an attempt to further improve on the current best solution found. The test set was used as a validation set during training. Some overfitting can be observed as the \acs{BHH} tried finding better solutions on the train set, but at the cost of generalisation on the test set. Minor divergence of the training loss is observed as the \acs{BHH} explores other heuristics in an attempt to improve performance. Since no move acceptance strategy, and no early stopping stategy was used, the \acs{BHH} could select heuristics that are sub-optimal. Future research opportunities should incorporate these aforementioned strategies.

\subsection{\acs{BHH} Baseline vs. Low-Level Heuristics}
\label{sec:conclusion:results:summary:standalone}

For this experimental group, three different configurations of the \acs{BHH} baseline configuration were implemented. These configurations vary in the type of \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool. The \textit{bhh\_all} configuration included all low-level \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool. The \textit{bhh\_gd} configuration included only gradient-based \index{heuristic}heuristics in the \index{heuristic pool}heuristic pool, and the \textit{bhh\_mh} configuration included only \index{meta-heuristic}meta-heuristics in the \index{heuristic pool}heuristic pool.

Overall the \textit{bhh\_gd} configuration performed the best out of the \acs{BHH} variants, achieving an overall rank of fourth amongst thirteen \index{heuristic}heuristics that were implemented and executed on fourteen datasets. The \textit{bhh\_gd} configuration produced performance results close to that of the best low-level \index{heuristic}heuristics and was only statistically outperformed by the top two low-level \index{heuristic}heuristics. The \textit{bhh\_all} configuration achieved an overall rank of sixth and the \textit{bhh\_mh} achieved an overall rank of eighth.

Although the \textit{bhh\_gd} configuration produced performance results comparable to the best low-level heuristics, the \textit{bhh\_all} and \textit{bhh\_mh} configurations produced average results. It was found that, in general, gradient-based heuristics produced the best results, as such, it it understandable that the \textit{bhh\_gd}  yielded the best performance outcomes between the different \acs{BHH} variants that were implemented. Although the \acs{BHH} variants were not able to produce better results than the top low-level \index{heuristic}heuristics, the \acs{BHH} variants still effectively trained the underlying \acp{FFNN} and produced good training outcomes overall.

It was shown that the \textit{bhh\_gd} configuration produced the lowest variance in rank between datasets out of all of the \index{heuristic}heuristics implemented, giving the \acs{BHH} the ability to generalise well to other problems.
